\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Designing with the Mind in Mind},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother



% Stuff I added.
% --------------

\usepackage{indentfirst}
\usepackage[doublespacing]{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{layout}   
\lhead{\sc Reading Summary}
\chead{}
\rhead{\thepage}
\lfoot{}
\cfoot{}
\rfoot{}

\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}

\usepackage{sectsty}
\sectionfont{\centering}
\subsectionfont{\centering}

\newtheorem{hypothesis}{Hypothesis}

% Begin document
% --------------

\begin{document}

\doublespacing

\begin{titlepage}
    \begin{center}
    \line(1,0){300} \\ 
    [0.25in]
    \huge{\bfseries Designing with the Mind in Mind} \\
    [2mm]
    \line(1,0){200} \\
    [1.5cm] 
    \textsc{\Large Chapters 4, 5 and 6} \\
    [0.75cm]
    \textsc{\Large Reading Summary} \\
    [9cm]
    \end{center}
    
    \begin{flushright}
    \textsc{\Large{Gurpreet Singh \\}\normalsize\emph{\ January 21, 2018 \\}\normalsize\emph{CS4474 \\} }
    
    \end{flushright}

\end{titlepage}

\newpage
\shipout\null

\hypertarget{chapter-4}{%
\section{Chapter 4}\label{chapter-4}}

\hypertarget{reading-is-unnatural}{%
\subsection{Reading is Unnatural}\label{reading-is-unnatural}}

\hypertarget{wired-for-language-not-reading}{%
\subsubsection{Wired for Language not
Reading}\label{wired-for-language-not-reading}}

We are born to speak languages and learn to speak quickly in our
childhood but when we get older it is as difficult as any other skill A
different brain area is used for this type of learning after childhood.
Most people learn how to speak but some people never learn how to read.
People may not be good at reading because of \{basically my problems
irl\}

Reading is teaching our brains how to recognize patterns. Morphemes are
combinations of letters we recognize and put together to make words

\hypertarget{feature-driven-vs-context-driven}{%
\subsubsection{Feature driven vs context
driven}\label{feature-driven-vs-context-driven}}

Feature driven is bottom up and sometimes called ``context free''. It
starts by identifying simple features like lines and uses them to make
complex objects like words. This type of reading is faster than context
driven despite instinct.

Context driven is top down and opposite of feature driven. You recognize
a morpheme, word or sentence and treat it like a single object to get
it's meaning. An example of this is something you would read often.
Mainly a backup method for reading.

\hypertarget{skilled-vs-unskilled-reading}{%
\subsubsection{Skilled vs Unskilled
reading}\label{skilled-vs-unskilled-reading}}

``Skilled readers'' use feature driven mostly and fallback to context
driven ``Unskilled readers'' use context driven because feature driven
is slow for them.

Not enough experience reading as a child causes unskilled reading

\hypertarget{poor-information-design-disprupts-reading}{%
\subsubsection{Poor information design disprupts
reading}\label{poor-information-design-disprupts-reading}}

Poor presentation can block reading for unskilled readers. The following
are things that disrupt reading:

\begin{itemize}
\tightlist
\item
  Uncommon words
\item
  Difficult scripts and typefaces
\item
  Tiny Fonts
\item
  Text on noisy background
\item
  Visual noise from too much text
\item
  Centered text is hard for eyes to follow
\end{itemize}

Any combination of the above can make for a very unreadable design
Support both reading styles by avoiding the problems listed above.

\hypertarget{most-reading-is-unnecessary}{%
\subsubsection{Most reading is
unnecessary}\label{most-reading-is-unnecessary}}

Most software has too much text in the instructions and people don't
read it anyway. You can be just as clear with less text. Provide a brief
overview and let users request more detail if they want.

\hypertarget{chapter-5}{%
\section{Chapter 5}\label{chapter-5}}

\hypertarget{our-color-vision-is-limited}{%
\subsection{Our Color Vision is
Limited}\label{our-color-vision-is-limited}}

\hypertarget{optimized-for-edge-contrast}{%
\subsubsection{Optimized for Edge
Contrast}\label{optimized-for-edge-contrast}}

We can see something better if it is high contrast and brightness isn't
as important

\hypertarget{discrimination-based-on-presentation}{%
\subsubsection{Discrimination based on
Presentation}\label{discrimination-based-on-presentation}}

\hypertarget{color-blindness}{%
\subsubsection{Color-Blindness}\label{color-blindness}}

\hypertarget{external-factors}{%
\subsubsection{External Factors}\label{external-factors}}

\hypertarget{guidelines-for-using-color}{%
\subsubsection{Guidelines for using
Color}\label{guidelines-for-using-color}}

\end{document}

